### 2017-10-06 writing/paper/sections/coincidences.tex
Some of reviewer 1s comments,change away from set partitions

We will consider the avoidance sets \(\av{\{\pi,p\}}\) where \(\pi\) is a classical pattern of length 3
and \(p\) is a mesh pattern of length 2 to establish sufficient conditions for two such
sets to be coincident. The classical pattern \(\pi\) will be fixed and called
the \emph{dominating pattern}.

@@

We now attempt to fully classify coincidences in families characterised by avoidance
of a classical pattern of length \(3\) and a mesh pattern of length \(2\), that is
finding and explaining all coincidences where \(\av{\{\pi,m\}} = \av{\{\pi,m^\prime\}}\),
where \(\pi\) is a classical pattern of length \(3\).

@@

\subsection{Coincidence classes of Av(\{321, (21, \textit{R})\})}
Through experimentation, considering avoidance of permutations of up to length \(11\), we discover
that there are at least \(29\) coincidence classes of mesh patterns with underlying classical
pattern \(21\).

>>>>

We will consider the avoidance sets \(\av{\pi,p}\) where \(\pi\) is a classical pattern of length 3
and \(p\) is a mesh pattern of length 2 to establish sufficient conditions for two such
sets to be coincident. The classical pattern \(\pi\) will be fixed and called
the \emph{dominating pattern}. Given such a dominating pattern \(\pi\) we will write \(q_1 \coinc{\pi} q_2\) if for the mesh patterns, \(q_1\) and \(q_2\),  the sets \(\av{p,q_1}\) and \(\av{p,q_2}\) are coincident.

Our first step is to calculate whether \(\av{p,q_1}\) and \(\av{p,q_2}\) are equal up to permutations of length 11 computationally, if they are we write \(q_1 \coinc[comp]{\pi} q_2\). If \(q_1 \coinc{\pi} q_2\), it can be seen that \(q_1 \coinc[comp]{\pi} q_2\), and therefore the \(\coinc{\pi}\)-equivalence classes form partitions of the \(\coinc[comp]{\pi}\)-coincidence classes.

@@

We now attempt to fully classify coincidences in families characterised by avoidance
of a classical pattern of length \(3\) and a mesh pattern of length \(2\), that is
finding and explaining all coincidences between mesh patterns \(m\) and \(m^\prime\), \(m\coinc{\pi} m^\prime\),
where \(\pi\) is a classical pattern of length \(3\).

@@

\subsection{Coincidence classes of Av(\{321, (21, \textit{R})\})}
Through experimentation, considering avoidance of permutations of up to length \(11\), we discover
that there are at least \(29\) \(\coinc[comp]{321}\)-coincidence classes where the underlying classical pattern of the mesh pattern is \(21\).

### 2017-10-06 writing/paper/sections/introduction.tex
Fix small fixes proposed by reviewer 2
Some of reviewer 1s comments,change away from set partitions

When considering permutation patterns some of the main questions posed relate to
how and when a pattern is avoided by, or contained in, an arbitrary set of
permutations. Two patterns \(\pi\) and \(\sigma\) are \emph{Wilf-equivalent} if
the number of permutations that avoid \(\pi\) of length \(n\) is equal to the
number of permutations that avoid \(\sigma\) of length \(n\). A stronger
equivalence condition is that of \emph{coincidence}, where the set of
permutations avoiding \(\pi\) is exactly equal to the set of permutations
avoiding \(\sigma\). Avoiding pairs of patterns of the same length with certain
properties has been studied, \textcite{MR2178749} considered avoiding
a pair of vincular patterns of length 3. \textcite{2015arXiv151203226B} study
avoiding a vincular and a covincular pattern simultaneously in order to achieve
some several counting results. However, little work has been done on
avoiding a mesh pattern and a classical pattern simultaneously.

In this work we aim to establish some ground in this field by computing
coincidences and Wilf-classes and calculating some of the enumerations of
avoiders of a mesh pattern of length 2 and a classical pattern of length 3. We
begin by establishing coincidences between mesh patterns of length 2 while
avoiding a classical pattern of length 3; this is used to establish sufficient
conditions for coincidence. We then establish Wilf-equivalence classes of these
coincidence classes where the classical pattern is \perm{2,3,1}.

>>>>

When considering permutation patterns some of the main questions posed relate to
how and when a pattern is avoided by, or contained in, an arbitrary set of
permutations. Two patterns \(\pi\) and \(\sigma\) are \emph{Wilf-equivalent} if
the number of permutations that avoid \(\pi\) of length \(n\) is equal to the
number of permutations that avoid \(\sigma\) of length \(n\). A stronger
equivalence condition is that of \emph{coincidence}, where the set of
permutations avoiding \(\pi\) is exactly equal to the set of permutations
avoiding \(\sigma\). Avoiding pairs of patterns of the same length with certain
properties has been studied, \textcite{MR2178749} considered avoiding
a pair of vincular patterns of length 3. \textcite{2015arXiv151203226B} study
avoiding a vincular and a covincular pattern simultaneously in order to achieve
several counting results. However, little work has been done on
avoiding a mesh pattern and a classical pattern simultaneously.

In this work we aim to establish some ground in this field by computing
coincidences and Wilf-classes and calculating some of the enumerations of
avoiders of a mesh pattern of length 2 and a classical pattern of length 3. We
begin by establishing coincidences between mesh patterns of length 2 while
avoiding a classical pattern of length 3 by computational methods, which are then
used to establish three ``Dominating Pattern Rules'' as well as some special cases
that can be used to calculate coincidences. We then use these coincidence classes
to calculate Wilf-equivalence classes showing some of the methods used.

### 2017-10-06 writing/paper/sections/wilf.tex
Some of reviewer 1s comments,change away from set partitions

When considering the Wilf-equivalences we consider how permutations correspond
to set-partitions.

\begin{definition} A \emph{set partition} of \(\nrange{n}\) is a set of non-empty subsets of \(\nrange{n}\)
such that \(\nrange{n}\) is a \emph{disjoint} union of these subsets.
\end{definition}

\begin{note}
  The avoiders of the mesh pattern \(q = %= \mperm{\perm{2,3,1}}{(1,0),(1,1),(1,2),(1,3)}
\textpattern{}{2,3,1}{1/0,1/1,1/2,1/3}\) in \(\mathfrak{S}_n\) are in one-to-one correspondence with partitions
of \(\nrange{n}\) (\textcite[Prop.~2]{DBLP:journals/ejc/Claesson01}).
I order to form this correspondence we read the permutation from left to right starting a
new block in the partition whenever we see an ascent.
\end{note}
\begin{example}
    The permutation \(\pi = \perm{5,4,2,1,3,9,6,8,7}\) corresponds to the
    partition \(\{\{5,4,2,1\},\{3\},\{9,6\},\{8,7\}\}\).
\end{example}

We will call the least element in each block the \emph{block-bottom}, and note that all permutations
in \(\av{\perm{2,3,1}}\) also avoid the mesh pattern \(q\), this classical pattern case
corresponds precisely to the non-crossing partitions.

We will use two main methods of establishing Wilf-equivalence between mesh patterns of length \(2\)
in \(\av{\perm{2,3,1}}\): the structural decomposition of avoiders, via generating functions; or the
structure of the set-partition induced by the pattern, looking at a particular occurrence of the
pattern in a permutation avoiding \(\perm{2,3,1}\). Sometimes it will be necessary to use both of
these methods to consolidate a single Wilf-class.

@@

First we prove the Wilf-equivalence between \(m_1\) and \(m_2\) shown in
\eqref{eq:singleud}, by considering the containers as set partitions.

Considering an occurrence of either of these patterns in a permutation  we know
the following about the points corresponding to the points in the patterns.
\begin{itemize}
    \item The point corresponding to the first point in both patterns
        must lie in the first block of the set partition (there are
        no points southwest from it in the permutation).
    \item The point corresponding to the second point in both patterns
        is a block bottom (there are no points southeast of it in
        the permutation).
    \item If the region corresponding to box \((2,2)\) in an occurrence of
    \(m_1\) is empty, then the point corresponding to the second point is
    precisely the last block bottom. If the region corresponding to box \((1,0)\)
    in an occurrence of \(m_2\) is empty, then the point corresponding to the
    second point is precisely the first block bottom.
    If these regions are non-empty then the block containing the point
    corresponding to the second point in both patterns contains only that point
    (it is a singleton block).
\end{itemize}

This means that permutations containing \(m_1\) correspond to set partitions
with a singleton block with value one higher than some element in the
block containing \(1\). The permutations containing \(m_2\) correspond
to the set partitions containing a block with block bottom having value
one lower than some element in the block containing \(1\) and if this
block is not the block containing \(1\) then it is a singleton block.
%%%%%%%%%%
%%%%%%%%%%
%%%%%%%%%%

The classes defined by containment of \(m_1\) and \(m_2\) inside \(\av{\perm{2,3,1}}\)are
equinumerous and therefore so are their avoiders.

>>>>

We will use two main methods of establishing Wilf-equivalence between mesh patterns of length \(2\)
in \(\av{\perm{2,3,1}}\): the structural decomposition of avoiders, via generating functions; or the
structure of a general permutation containing the pattern, looking at a particular occurrence of the
pattern in a permutation avoiding \(\perm{2,3,1}\). Sometimes it will be necessary to use both of
these methods to consolidate a single Wilf-class.

@@

First we prove the Wilf-equivalence between \(m_1\) and \(m_2\) shown in
\eqref{eq:singleud}, by considering the form of a general permutation containing
either of the two patterns. First looking at a general occurrence of \(m_1\) in a permutation
in \(\av{231}\)
\begin{equation*}
\begin{tikzpicture}[scale=1.0]
\modpattern[4]{}{1,2}{0/0,0/1,1/1,1/2,2/0,2/1}
\node at (0.5,2.5) {\Large \(A\)};
\node at (2.5,2.5) {\Large \(B\)};
\node at (1.5,0.5) {\Large \(C\)};
\end{tikzpicture}	
\end{equation*}

If there is an occurrence of \(m_1\) there must be a lowest occurrence of \(m_1\), \ie the occurrence has the lowest possible values for any occurrence. Now consider the top
regions, labelled \(A \et B\), the subpermutation contained in these regions must avoid the permutation \(231\). Also, the subpermutation in the region \(A\) must be a decreasing subsequence, otherwise an occurrence of \(231\) will be created with either of the points in the occurrence. Now, consider the region labelled \(C\), since we specified that we were focused on the lowest possible occurrence of \(m_1\) this region cannot contain an occurrence of either \(m_1\) or \(231\). We now have a structural decomposition of a container of \(m_1\) inside \(\av{231}\).

Now consider a general occurrence of \(m_2\) in a permutation
in \(\av{231}\)
\begin{equation*}
\begin{tikzpicture}[scale=1.0]
\modpattern[4]{}{2,1}{0/0,0/1,1/1,1/2,2/0,2/1}
\node at (0.5,2.5) {\Large \(A^\prime\)};
\node at (2.5,2.5) {\Large \(B^\prime\)};
\node at (1.5,0.5) {\Large \(C^\prime\)};
\end{tikzpicture}	
\end{equation*}

Similarly to a container of \(m_1\) we will look at the lowest possible occurrence of \(m_2\), similar to before the regions \(A^\prime \et B^\prime\) together contain an avoider of \(231\) and \(A\) contains a decreasing subsequence. Since we are considering the lowest occurrence of \(m_2\) so the region \(C^\prime\) does not contain an occurrence of either \(m_2\) or \(231\).

Since all the regions in both of these cases contain the same parts,  the classes defined by containment of \(m_1\) and \(m_2\) inside \(\av{\perm{2,3,1}}\) are
equinumerous and therefore so are their avoiders.
